### 2017-05-18 pkg/Pmisc/inst/docs/document.Rmd
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@1751 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

```{r theHeader, echo=FALSE}
Pmisc::markdownHeader(
  title="Example of a simple R markdown document with subfigures", 		
  author='Patrick Brown',
  bibliography = bibFile,
  geometry='margin=1in'
)
```

>>>>

```{r theHeader, echo=FALSE}
Pmisc::markdownHeader(
  title="Example of a simple R markdown document with subfigures", 		
  author='Patrick Brown',
  bibliography = bibFile,
  geometry='margin=1in'
)

# consider adding
automatic-styles = '<style:style style:name="OLE" style:family="graphic"><style:graphic-properties text:anchor-type="paragraph" style:wrap="none"/></style:style>'
# to make equations better in odt document
```
